The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

Over the course of a decade,\
the first all-sky X-ray survey with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
extending about twice as large as the \textit{Fermi} bubbles.\
The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.

@@

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric \textit{Fermi} and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to\
the rotation axis of a galatic plane (disc normal, hereafter).\
In contrast, a number of galaxies in which the jets are oblique to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disc without jet source.\
             The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

@@

 \Cref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middile), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction.

@@

 Finally, the comparison between\
 \Cref{fig__jetI5+ismSeed3-45deg}\
 and\
 \Cref{fig__jetI5+ismSeed3-45deg-CR}\
 shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
 bringing the the pressure ratio of CR to gas is 0.1--0.2,
 similar to 0.18 at the begining of the simulation.
 We thefore stress that\
 ignoring the contribution of CR pressure gradient to the momentum of the gas\
 in \Cref{governing-eq} is resonable.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     bringing the the pressure ratio of CR to gas is 0.1--0.2,
     similar to 0.18 at the begining of the simulation.
     We thefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in \Cref{governing-eq} is resonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}

>>>>

Over the course of a decade,\
the first all-sky X-ray survey with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
extending about twice as large as the \textit{Fermi} bubbles.\
The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kpc across \citep{Predehl2021},
and displays morphological symmetry about the Galactic plane as the \textit{Fermi} bubbles.

@@

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric \textit{Fermi} and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to\
the rotation axis of a galactic plane (disc normal, hereafter).\
In contrast, a number of galaxies in which the jets are oblique to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

@@

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disc without jet source.\
             The vertical bands from left to right depict the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold neutral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

@@

 \Cref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middle), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction.

@@

 Finally, the comparison between\
 \Cref{fig__jetI5+ismSeed3-45deg}\
 and\
 \Cref{fig__jetI5+ismSeed3-45deg-CR}\
 shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
 bringing the pressure ratio of CR to gas is 0.1--0.2,
 similar to 0.18 at the beginning of the simulation.
 We therefore stress that\
 ignoring the contribution of CR pressure gradient to the momentum of the gas\
 in \Cref{governing-eq} is reasonable.

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg-CR.png}
    \caption{
     The CR pressure slice passing through the jet source at 12.39 Myr.\
     Comparison between\
     gas pressure (\Cref{fig__jetI5+ismSeed3-45deg}) and cosmic ray pressure\
     shows that
     the CR pressure\
     is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$,\
     bringing the pressure ratio of CR to gas is 0.1--0.2,
     similar to 0.18 at the beginning of the simulation.
     We therefore stress that\
     ignoring the contribution of CR pressure gradient to the momentum of the gas\
     in \Cref{governing-eq} is reasonable.
     }
    \label{fig__jetI5+ismSeed3-45deg-CR}
  \end{figure}
